Predictions for detecting BHNS and other double compact objects binaries with LISA

### 2021-04-10 paper/tex/sections/appendix.tex
reorganise results: table to appendix, sc plot sooner

\section{Derivation of Strain and SNR Equations}\label{app:strain_snr_deriv}
In this section we provide a full derivation/explanation of how we arrived at the equations used in our simulations.

\subsection{Conversions and definitions}
Each of these conversions and definitions are useful in the later derivations and we define them here for convenience. First, we define the chirp mass of a binary as 
\begin{equation}\label{eq:chirpmass}
    \mathcal{M}_c = \frac{(m_1 m_2)^{3/5}}{(m_1 + m_2)^{1/5}},
\end{equation}
where $m_1$ and $m_2$ are the primary and secondary mass of the binary. Kepler's third law is well known and allows one to convert between orbital frequency and the semi-major axis of a binary. For convenience we show it here
\begin{equation}\label{eq:kepler3rd}
    a = \qty(\frac{G(m_1 + m_2)}{(2 \pi f_{\rm orb})^{2}})^{1/3},\qquad f_{\rm orb} = \frac{1}{2 \pi} \sqrt{\frac{G(m_1 + m_2)}{a^3}}.
\end{equation}
As we deal with eccentric binaries, the different harmonic frequencies of gravitational wave emission become important. We therefore write that the relative power radiated into the $n^{\rm th}$ harmonic for a binary with eccentricity $e$ is \citep[][Eq.\,20]{Peters+1963}
\begin{equation}\label{eq:g(n,e)}
    \begin{aligned}
        g(n, e) = \frac{n^{4}}{32} & \left\{ \left[ J_{n-2}(n e)-2 e J_{n-1}(n e)+\frac{2}{n} J_{n}(n e)+2 e J_{n+1}(n e)-J_{n+2}(n e)\right]^{2}\right.\\
        &\left.+\left(1-e^{2}\right)\left[J_{n-2}(n e)-2 J_{n}(n e)+J_{n+2}(n e)\right]^{2}+\frac{4}{3 n^{2}}\left[J_{n}(n e)\right]^{2}\right\},
    \end{aligned}
\end{equation}
where $J_{n}(v)$ is the Bessel function of the first kind. Thus, the sum of $g(n, e)$ over all harmonics gives the factor by which the gravitational wave emission is stronger for a binary of eccentricity $e$ over an otherwise identical circular binary. This enhancement factor is defined by Peters as \citep[][Eq.\,17]{Peters+1963}
\begin{equation}\label{eq:eccentricity_enhancement_factor}
    F(e) = \frac{1 + (73 / 24) e^2 + (37 / 96) e^4}{(1 - e^2)^{7/2}}.
\end{equation}
Note that $F(0) = 1$ as one would expect. A fun number to remember is that $F(0.5) \approx 5.0$, or in words, a binary with eccentricity $0.5$ loses energy to gravitational waves at a rate $5$ times higher than a similar circular binary.

\subsection{Characteristic Strain}
The characteristic strain from a binary in the $n^{\rm th}$ harmonic is defined as follows (e.g. \citealp[][Eq.\,56]{Barack+2004}; \citealp[][Eq.\,5.1]{ Flanagan+1998})
\begin{equation}\label{eq:char_strain_dedf}
    h_{c,n}^2 = \frac{1}{(\pi D_L)^2} \qty( \frac{2 G}{c^3} \frac{\dot{E_n}}{\dot{f_n}} ),
\end{equation}
where $D_L$ is the luminosity distance to the binary, $\dot{E}_n$ is the power radiated in the $n^{\rm th}$ harmonic and $\dot{f}_n$ is the rate of change of the $n^{\rm th}$ harmonic frequency. The power radiated in the $n^{\rm th}$ harmonic is given by \citep[][Eq. 19]{Peters+1963}
\begin{equation}\label{eq:edot_peters}
    \dot{E}_n = \frac{32}{5} \frac{G^{4}}{c^5} \frac{m_{1}^{2} m_{2}^{2}\left(m_{1}+m_{2}\right)}{a^{5}} g(n, e),
\end{equation}
where $m_1$ is the primary mass, $m_2$ is the secondary mass, $a$ is the semi-major axis of the binary and $e$ is the eccentricity. Using \eqref{eq:chirpmass} and \ref{eq:kepler3rd}, we can recast \eqref{eq:edot_peters} in a form more applicable for gravitational wave detections that is a function of only the chirp mass, orbital frequency and eccentricity.
\begin{align}
    \dot{E}_n &= \frac{32}{5} \frac{G^{4}}{c^5} \qty(m_{1}^{2} m_{2}^{2}\left(m_{1}+m_{2}\right)) g(n, e) \cdot \qty(\frac{(2 \pi f_{\rm orb})^{2}}{G(m_1 + m_2)})^{5/3} \\
    \dot{E}_n &= \frac{32}{5} \frac{G^{7/3}}{c^5} \frac{m_{1}^{2} m_{2}^{2}}{\left(m_{1}+m_{2}\right)^{2/3}} (2 \pi f_{\rm orb})^{10/3} g(n, e) \\
    \dot{E}_n(\mathcal{M}_c, f_{\rm orb}, e) &= \frac{32}{5} \frac{G^{7 / 3}}{c^{5}}\left(2 \pi f_{\mathrm{orb}} \mathcal{M}_{c}\right)^{10 / 3} g(n, e) \label{eq:edot}
\end{align}
The last term needed to define the characteristic strain in \eqref{eq:char_strain_dedf} is the rate of change of the $n^{\rm th}$ harmonic frequency. We can first apply the chain rule and note that
\begin{equation}\label{eq:fdot_chainrule}
    \dot{f}_{n} = \dv{f_{n}}{a} \dv{a}{t}.
\end{equation}
The frequency of the $n^{\rm th}$ harmonic is simply defined as $f_n = n \cdot f_{\rm orb}$ and therefore we can find an expression for $\dd{f_{n}} / \dd{a}$ by rearranging and differentiating \eqref{eq:kepler3rd}
\begin{align}
    f_{n} &= \frac{n}{2 \pi} \sqrt{\frac{G(m_1 + m_2)}{a^3}}, \\
    \dv{f_{n}}{a} &= -\frac{3 n}{4 \pi} \frac{\sqrt{G(m_1 + m_2)}}{a^{5/2}}. \label{eq:dfda}
\end{align}
The rate at which the semi-major axis decreases is \citep[][Eq. 5.6]{Peters+1964}
\begin{equation}\label{eq:dadt}
    \dv{a}{t} = -\frac{64}{5} \frac{G^{3} m_{1} m_{2}\left(m_{1}+m_{2}\right)}{c^{5} a^{3}} F(e).
\end{equation}
Substituting \eqref{eq:dfda} and \ref{eq:dadt} into \eqref{eq:fdot_chainrule} gives an expression for $\dot{f}_{n}$
\begin{align}
    \dot{f}_n &= -\frac{3 n}{4 \pi} \frac{\sqrt{G(m_1 + m_2)}}{a^{5/2}} \cdot -\frac{64}{5} \frac{G^{3} m_{1} m_{2}\left(m_{1}+m_{2}\right)}{c^{5} a^{3}} F(e), \\
    \dot{f}_n &= \frac{48 n}{5 \pi} \frac{G^{7/2}}{c^5} \qty(m_1 m_2 (m_1 + m_2)^{3/2}) \frac{F(e)}{a^{11/2}},
\end{align}
which, as above with $\dot{E}_n$, we can recast using Kepler's third law and the definition of the chirp mass
\begin{align}
    \dot{f}_n &= \frac{48 n}{5 \pi} \frac{G^{7/2}}{c^5} \qty(m_1 m_2 (m_1 + m_2)^{3/2}) F(e) \cdot \qty(\frac{(2 \pi f_{\rm orb})^{2}}{G(m_1 + m_2)})^{11/6}, \\
    &= \frac{48 n}{5 \pi} \frac{G^{5/3}}{c^5} \frac{m_1 m_2}{(m_1 + m_2)^{1/3}} \cdot (2 \pi f_{\rm orb})^{11/3} \cdot F(e), \\
    \dot{f}_n(\mathcal{M}_c, f_{\rm orb}, e) &= \frac{48 n}{5 \pi} \frac{\qty(G \mathcal{M}_c)^{5/3}}{c^5} (2 \pi f_{\rm orb})^{11/3} F(e) \label{eq:fdot}
\end{align}
With definitions of both $\dot{E}_n$ and $\dot{f}_n$, we are now in a position to find an expression for the characteristic strain by plugging \eqref{eq:edot} and \ref{eq:fdot} into \ref{eq:char_strain}:
\begin{align}
    h^2_{c,n} &= \frac{1}{(\pi D_L)^2} \qty( \frac{2 G}{c^3} \frac{\frac{32}{5} \frac{G^{7 / 3}}{c^{5}}\left(2 \pi f_{\mathrm{orb}} \mathcal{M}_{c}\right)^{10 / 3} g(n, e)}{\frac{48 n}{5 \pi} \frac{\qty(G \mathcal{M}_c)^{5/3}}{c^5} (2 \pi f_{\rm orb})^{11/3} F(e)} ) \\
    &= \frac{1}{(\pi D_L)^2} \qty( \frac{2^{5/3} \pi^{2/3}}{3} \frac{(G \mathcal{M}_c)^{5/3}}{c^3} \frac{1}{f_{\rm orb}^{1/3}} \frac{g(n, e)}{n F(e)} ) \\
    h_{c,n}^2(\mathcal{M}_c, D_L, f_{\rm orb}, e) &= \frac{2^{5/3}}{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{f_{\rm orb}^{1/3}} \frac{g(n, e)}{n F(e)} \label{eq:char_strain}
\end{align}

\subsection{Strain}
The strain can be found by dividing the characteristic strain by the square root of twice the number of cycles. This is explained in \citet{Finn+2000} and in further detail in \citet{Moore+2015}. The physical reasoning behind the idea is that the binary will spend a certain amount of time in the vicinity of some frequency $f$ and cause a similar gravitational wave strain. This leads to the signal 'accumulating' and resulting in a larger signal-to-noise ratio. Therefore, the characteristic strain represents the strain measured by the detector over the duration of the mission, whilst the strain is what is emitted by the binary at each instantaneous moment.

Following this logic, we can convert between characteristic strain and strain with \citep[e.g][see text before Eq.\,2.2]{Finn+2000}
\begin{equation}\label{eq:strain-to-charstrain}
    h_{c, n}^2 = \qty(\frac{2 f_n^2}{\dot{f}_n}) h_n^2.
\end{equation}
Therefore, using this, in addition to Eq. \ref{eq:fdot} and Eq. \ref{eq:char_strain}, we can write an expression for the strain amplitude of gravitational waves in the $n^{\rm th}$ harmonic
\begin{align}
    h_n^2 &= \qty(\frac{\dot{f}_n}{2 f_n^2}) h_{c, n}^2, \\
    h_n^2 &= \qty(\frac{48 n}{5 \pi} \frac{\qty(G \mathcal{M}_c)^{5/3}}{c^5} (2 \pi f_{\rm orb})^{11/3} F(e) \cdot \frac{1}{2 n^2 f_{\rm orb}^2}) \qty(\frac{2^{5/3}}{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{n f_{\rm orb}^{1/3}} \frac{g(n, e)}{F(e)}), \\
    h_n^2(\mathcal{M}_c, f_{\rm orb}, D_L, e) &= \frac{2^{25/3}}{5} \frac{(G \mathcal{M}_c)^{10/3}}{c^8 D_L^2} \frac{g(n, e)}{n^2} \qty(\pi f_{\rm orb})^{4/3} . \label{eq:strain}
\end{align}

\subsection{General Signal-to-Noise Ratio}
We can start at the equation for the general signal-to-noise ratio from \citet{Flanagan+1998} (Eq. 2.30)
\begin{equation}
    \left\langle\rho^{2}\right\rangle=\frac{2(1+z)^{2}}{5 \pi^{2} D_L(z)^{2}} \int_{0}^{\infty} d f \frac{1}{f^{2} S_{n}(f)} \dv{E}{f}[(1 + z) f],
\end{equation}
where $z$ is the redshift. We need to adjust this equation in a couple of key ways for LISA Galactic binaries. First we multiply by 5 because of the way the signal response function is defined in LISA (converse to LIGO) -- \citet[see][]{Robson+2019} for a good explanation. Additionally we can set $z = 0$ for Galactic binaries, convert to SI units from geometric units (as is our convention in this document) and integrate over specific frequency limits.
\begin{equation}\label{eq:snr_abs}
    \avg{\rho_n^2} = \int_{f_{n, i}}^{f_{n, f}} \underbrace{\frac{2 G}{\pi^2 c^3 D_L^2} \dv{E_n}{f_n}}_{\text{signal}} \underbrace{\frac{1}{f_n^2 S_{\rm n}(f_n)}}_{\text{noise}} \dd{f_n}.
\end{equation}
It is now useful to inspect the `signal' term in the equation. We can do this specifically by first finding an expression for $\dd{E_n}/\dd{f_n}$ through the chain rule. We can write
\begin{equation}\label{eq:dedf}
    \dv{E_n}{f_n} = \dv{E_n}{t} \dv{a}{f_n} \dv{t}{a},
\end{equation}
where each term respectively comes from \eqref{eq:edot_peters}, the inverse of \eqref{eq:dfda} and the inverse of \eqref{eq:dadt}.
We can substitute these into Eq. \ref{eq:dedf} and simplify as follows
\begin{align}
    \dv{E_n}{f_n} &= \frac{32}{5} \frac{G^{4}}{c^5} \frac{m_1^2 m_2^2 \qty(m_1 + m_2)}{a^5} g(n, e) \cdot -\frac{4 \pi}{3 n} \frac{a^{5/2}}{(G(m_1 + m_2))^{1/2}} \cdot -\frac{5}{64} \frac{c^5 a^3}{G^3 m_1 m_2 (m_1 + m_2)} \frac{1}{F(e)}, \\
    &= \frac{2 \pi}{3} \frac{G^{1/2} m_1 m_2}{(m_1 + m_2)^{1/2}} \frac{g(n, e)}{n F(e)} \cdot a^{1/2}, \\
    &= \frac{2 \pi}{3} \frac{G^{1/2} m_1 m_2}{(m_1 + m_2)^{1/2}} \frac{g(n, e)}{n F(e)} \cdot \qty(\frac{G(m_1 + m_2)}{(2 \pi f_{\rm orb})^2})^{1/6}, \\
    &= \frac{2^{2/3} \pi^{2/3}}{3} \frac{G^{2/3} m_1 m_2}{(m_1 + m_2)^{1/3}} \frac{g(n, e)}{n F(e)} \cdot f_{\rm orb}^{-1/3}, \\
    \dv{E_n}{f_n} &= \frac{2^{2/3} \pi^{2/3}}{3} G^{2/3} \mathcal{M}^{5/3} \frac{g(n, e)}{n F(e)} \cdot f_{\rm orb}^{-1/3}.
\end{align}
If we further multiply this by the prefactor in \eqref{eq:snr_abs}, we arrive at an expression for the `signal' portion of the equation, which notably is exactly the square of the characteristic strain (see \eqref{eq:char_strain}).
\begin{equation}
    \dv{E_n}{f_n} \frac{2 G}{\pi^2 c^3 D_L^2} = \frac{2^{5/3} }{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{n f_{\rm orb}^{1/3}} \frac{g(n, e)}{F(e)} = h_{c,n}^2.
\end{equation}
We can therefore write that the sky-averaged signal-to-noise ratio for a Galactic binary is
\begin{equation}\label{eq:snr_general}
    \boxed{ \rho^2 = \sum_{n=1}^{\infty}  \int_{f_{n, i}}^{f_{n, f}} \frac{h_{c, n}^2}{f_n^2 S_{\rm n}(f_n)} \dd{f_n}. }
\end{equation}

\subsection{Stationary Signal-to-Noise Ratio}
For our sample, it was extremely useful to note that the vast majority of our binaries were stationary in frequency space on the timescale of a space-based observing mission. In this case, the start and end frequencies are only separated by a very small $\Delta f_n$ and so we can make the approximation that
\begin{align}
    \rho_n^2 &= \lim_{\Delta f \to 0} \int_{f_{n}}^{f_{n} + \Delta f_n} \frac{h_{c, n}^2}{f_n^2 S_n(f_n)} \dd{f_n}, \nonumber \\
    &\approx \frac{\Delta f_n \cdot h_{c, n}^2}{f_n^2 S_n(f_n)}.
\end{align}
Moreover, we can immediately write that $\Delta f_n = \dot{f}_n \Delta T$, where we know that $\Delta T = T_{\rm obs}$, such that
\begin{equation}
    \rho_n^2 = \left(\frac{\dot{f}_n}{f_n^2} h_{c, n}^2 \right) \frac{T_{\rm obs}}{S_n(f_n)},
\end{equation}
where the term in parentheses can be replaced with $2 h_n^2$ using Equation \ref{eq:strain-to-charstrain}. This gives the final expression for the signal-to-noise ratio when the stationary approximation is applied (as shown in Equation \ref{eq:snr_stat})
\begin{equation}
    \rho_{\rm stat}^2 = \sum_{n=1}^{\infty} \frac{2 T_{\rm obs} h_n^2}{S_n(f_n)} .
\end{equation}

@@

\section{Supplementary figures}

>>>>

% \section{Derivation of Strain and SNR Equations}\label{app:strain_snr_deriv}
% In this section we provide a full derivation/explanation of how we arrived at the equations used in our simulations.

% \subsection{Conversions and definitions}
% Each of these conversions and definitions are useful in the later derivations and we define them here for convenience. First, we define the chirp mass of a binary as 
% \begin{equation}\label{eq:chirpmass}
%     \mathcal{M}_c = \frac{(m_1 m_2)^{3/5}}{(m_1 + m_2)^{1/5}},
% \end{equation}
% where $m_1$ and $m_2$ are the primary and secondary mass of the binary. Kepler's third law is well known and allows one to convert between orbital frequency and the semi-major axis of a binary. For convenience we show it here
% \begin{equation}\label{eq:kepler3rd}
%     a = \qty(\frac{G(m_1 + m_2)}{(2 \pi f_{\rm orb})^{2}})^{1/3},\qquad f_{\rm orb} = \frac{1}{2 \pi} \sqrt{\frac{G(m_1 + m_2)}{a^3}}.
% \end{equation}
% As we deal with eccentric binaries, the different harmonic frequencies of gravitational wave emission become important. We therefore write that the relative power radiated into the $n^{\rm th}$ harmonic for a binary with eccentricity $e$ is \citep[][Eq.\,20]{Peters+1963}
% \begin{equation}\label{eq:g(n,e)}
%     \begin{aligned}
%         g(n, e) = \frac{n^{4}}{32} & \left\{ \left[ J_{n-2}(n e)-2 e J_{n-1}(n e)+\frac{2}{n} J_{n}(n e)+2 e J_{n+1}(n e)-J_{n+2}(n e)\right]^{2}\right.\\
%         &\left.+\left(1-e^{2}\right)\left[J_{n-2}(n e)-2 J_{n}(n e)+J_{n+2}(n e)\right]^{2}+\frac{4}{3 n^{2}}\left[J_{n}(n e)\right]^{2}\right\},
%     \end{aligned}
% \end{equation}
% where $J_{n}(v)$ is the Bessel function of the first kind. Thus, the sum of $g(n, e)$ over all harmonics gives the factor by which the gravitational wave emission is stronger for a binary of eccentricity $e$ over an otherwise identical circular binary. This enhancement factor is defined by Peters as \citep[][Eq.\,17]{Peters+1963}
% \begin{equation}\label{eq:eccentricity_enhancement_factor}
%     F(e) = \frac{1 + (73 / 24) e^2 + (37 / 96) e^4}{(1 - e^2)^{7/2}}.
% \end{equation}
% Note that $F(0) = 1$ as one would expect. A fun number to remember is that $F(0.5) \approx 5.0$, or in words, a binary with eccentricity $0.5$ loses energy to gravitational waves at a rate $5$ times higher than a similar circular binary.

% \subsection{Characteristic Strain}
% The characteristic strain from a binary in the $n^{\rm th}$ harmonic is defined as follows (e.g. \citealp[][Eq.\,56]{Barack+2004}; \citealp[][Eq.\,5.1]{ Flanagan+1998})
% \begin{equation}\label{eq:char_strain_dedf}
%     h_{c,n}^2 = \frac{1}{(\pi D_L)^2} \qty( \frac{2 G}{c^3} \frac{\dot{E_n}}{\dot{f_n}} ),
% \end{equation}
% where $D_L$ is the luminosity distance to the binary, $\dot{E}_n$ is the power radiated in the $n^{\rm th}$ harmonic and $\dot{f}_n$ is the rate of change of the $n^{\rm th}$ harmonic frequency. The power radiated in the $n^{\rm th}$ harmonic is given by \citep[][Eq. 19]{Peters+1963}
% \begin{equation}\label{eq:edot_peters}
%     \dot{E}_n = \frac{32}{5} \frac{G^{4}}{c^5} \frac{m_{1}^{2} m_{2}^{2}\left(m_{1}+m_{2}\right)}{a^{5}} g(n, e),
% \end{equation}
% where $m_1$ is the primary mass, $m_2$ is the secondary mass, $a$ is the semi-major axis of the binary and $e$ is the eccentricity. Using \eqref{eq:chirpmass} and \ref{eq:kepler3rd}, we can recast \eqref{eq:edot_peters} in a form more applicable for gravitational wave detections that is a function of only the chirp mass, orbital frequency and eccentricity.
% \begin{align}
%     \dot{E}_n &= \frac{32}{5} \frac{G^{4}}{c^5} \qty(m_{1}^{2} m_{2}^{2}\left(m_{1}+m_{2}\right)) g(n, e) \cdot \qty(\frac{(2 \pi f_{\rm orb})^{2}}{G(m_1 + m_2)})^{5/3} \\
%     \dot{E}_n &= \frac{32}{5} \frac{G^{7/3}}{c^5} \frac{m_{1}^{2} m_{2}^{2}}{\left(m_{1}+m_{2}\right)^{2/3}} (2 \pi f_{\rm orb})^{10/3} g(n, e) \\
%     \dot{E}_n(\mathcal{M}_c, f_{\rm orb}, e) &= \frac{32}{5} \frac{G^{7 / 3}}{c^{5}}\left(2 \pi f_{\mathrm{orb}} \mathcal{M}_{c}\right)^{10 / 3} g(n, e) \label{eq:edot}
% \end{align}
% The last term needed to define the characteristic strain in \eqref{eq:char_strain_dedf} is the rate of change of the $n^{\rm th}$ harmonic frequency. We can first apply the chain rule and note that
% \begin{equation}\label{eq:fdot_chainrule}
%     \dot{f}_{n} = \dv{f_{n}}{a} \dv{a}{t}.
% \end{equation}
% The frequency of the $n^{\rm th}$ harmonic is simply defined as $f_n = n \cdot f_{\rm orb}$ and therefore we can find an expression for $\dd{f_{n}} / \dd{a}$ by rearranging and differentiating \eqref{eq:kepler3rd}
% \begin{align}
%     f_{n} &= \frac{n}{2 \pi} \sqrt{\frac{G(m_1 + m_2)}{a^3}}, \\
%     \dv{f_{n}}{a} &= -\frac{3 n}{4 \pi} \frac{\sqrt{G(m_1 + m_2)}}{a^{5/2}}. \label{eq:dfda}
% \end{align}
% The rate at which the semi-major axis decreases is \citep[][Eq. 5.6]{Peters+1964}
% \begin{equation}\label{eq:dadt}
%     \dv{a}{t} = -\frac{64}{5} \frac{G^{3} m_{1} m_{2}\left(m_{1}+m_{2}\right)}{c^{5} a^{3}} F(e).
% \end{equation}
% Substituting \eqref{eq:dfda} and \ref{eq:dadt} into \eqref{eq:fdot_chainrule} gives an expression for $\dot{f}_{n}$
% \begin{align}
%     \dot{f}_n &= -\frac{3 n}{4 \pi} \frac{\sqrt{G(m_1 + m_2)}}{a^{5/2}} \cdot -\frac{64}{5} \frac{G^{3} m_{1} m_{2}\left(m_{1}+m_{2}\right)}{c^{5} a^{3}} F(e), \\
%     \dot{f}_n &= \frac{48 n}{5 \pi} \frac{G^{7/2}}{c^5} \qty(m_1 m_2 (m_1 + m_2)^{3/2}) \frac{F(e)}{a^{11/2}},
% \end{align}
% which, as above with $\dot{E}_n$, we can recast using Kepler's third law and the definition of the chirp mass
% \begin{align}
%     \dot{f}_n &= \frac{48 n}{5 \pi} \frac{G^{7/2}}{c^5} \qty(m_1 m_2 (m_1 + m_2)^{3/2}) F(e) \cdot \qty(\frac{(2 \pi f_{\rm orb})^{2}}{G(m_1 + m_2)})^{11/6}, \\
%     &= \frac{48 n}{5 \pi} \frac{G^{5/3}}{c^5} \frac{m_1 m_2}{(m_1 + m_2)^{1/3}} \cdot (2 \pi f_{\rm orb})^{11/3} \cdot F(e), \\
%     \dot{f}_n(\mathcal{M}_c, f_{\rm orb}, e) &= \frac{48 n}{5 \pi} \frac{\qty(G \mathcal{M}_c)^{5/3}}{c^5} (2 \pi f_{\rm orb})^{11/3} F(e) \label{eq:fdot}
% \end{align}
% With definitions of both $\dot{E}_n$ and $\dot{f}_n$, we are now in a position to find an expression for the characteristic strain by plugging \eqref{eq:edot} and \ref{eq:fdot} into \ref{eq:char_strain}:
% \begin{align}
%     h^2_{c,n} &= \frac{1}{(\pi D_L)^2} \qty( \frac{2 G}{c^3} \frac{\frac{32}{5} \frac{G^{7 / 3}}{c^{5}}\left(2 \pi f_{\mathrm{orb}} \mathcal{M}_{c}\right)^{10 / 3} g(n, e)}{\frac{48 n}{5 \pi} \frac{\qty(G \mathcal{M}_c)^{5/3}}{c^5} (2 \pi f_{\rm orb})^{11/3} F(e)} ) \\
%     &= \frac{1}{(\pi D_L)^2} \qty( \frac{2^{5/3} \pi^{2/3}}{3} \frac{(G \mathcal{M}_c)^{5/3}}{c^3} \frac{1}{f_{\rm orb}^{1/3}} \frac{g(n, e)}{n F(e)} ) \\
%     h_{c,n}^2(\mathcal{M}_c, D_L, f_{\rm orb}, e) &= \frac{2^{5/3}}{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{f_{\rm orb}^{1/3}} \frac{g(n, e)}{n F(e)} \label{eq:char_strain}
% \end{align}

% \subsection{Strain}
% The strain can be found by dividing the characteristic strain by the square root of twice the number of cycles. This is explained in \citet{Finn+2000} and in further detail in \citet{Moore+2015}. The physical reasoning behind the idea is that the binary will spend a certain amount of time in the vicinity of some frequency $f$ and cause a similar gravitational wave strain. This leads to the signal 'accumulating' and resulting in a larger signal-to-noise ratio. Therefore, the characteristic strain represents the strain measured by the detector over the duration of the mission, whilst the strain is what is emitted by the binary at each instantaneous moment.

% Following this logic, we can convert between characteristic strain and strain with \citep[e.g][see text before Eq.\,2.2]{Finn+2000}
% \begin{equation}\label{eq:strain-to-charstrain}
%     h_{c, n}^2 = \qty(\frac{2 f_n^2}{\dot{f}_n}) h_n^2.
% \end{equation}
% Therefore, using this, in addition to Eq. \ref{eq:fdot} and Eq. \ref{eq:char_strain}, we can write an expression for the strain amplitude of gravitational waves in the $n^{\rm th}$ harmonic
% \begin{align}
%     h_n^2 &= \qty(\frac{\dot{f}_n}{2 f_n^2}) h_{c, n}^2, \\
%     h_n^2 &= \qty(\frac{48 n}{5 \pi} \frac{\qty(G \mathcal{M}_c)^{5/3}}{c^5} (2 \pi f_{\rm orb})^{11/3} F(e) \cdot \frac{1}{2 n^2 f_{\rm orb}^2}) \qty(\frac{2^{5/3}}{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{n f_{\rm orb}^{1/3}} \frac{g(n, e)}{F(e)}), \\
%     h_n^2(\mathcal{M}_c, f_{\rm orb}, D_L, e) &= \frac{2^{25/3}}{5} \frac{(G \mathcal{M}_c)^{10/3}}{c^8 D_L^2} \frac{g(n, e)}{n^2} \qty(\pi f_{\rm orb})^{4/3} . \label{eq:strain}
% \end{align}

% \subsection{General Signal-to-Noise Ratio}
% We can start at the equation for the general signal-to-noise ratio from \citet{Flanagan+1998} (Eq. 2.30)
% \begin{equation}
%     \left\langle\rho^{2}\right\rangle=\frac{2(1+z)^{2}}{5 \pi^{2} D_L(z)^{2}} \int_{0}^{\infty} d f \frac{1}{f^{2} S_{n}(f)} \dv{E}{f}[(1 + z) f],
% \end{equation}
% where $z$ is the redshift. We need to adjust this equation in a couple of key ways for LISA Galactic binaries. First we multiply by 5 because of the way the signal response function is defined in LISA (converse to LIGO) -- \citet[see][]{Robson+2019} for a good explanation. Additionally we can set $z = 0$ for Galactic binaries, convert to SI units from geometric units (as is our convention in this document) and integrate over specific frequency limits.
% \begin{equation}\label{eq:snr_abs}
%     \avg{\rho_n^2} = \int_{f_{n, i}}^{f_{n, f}} \underbrace{\frac{2 G}{\pi^2 c^3 D_L^2} \dv{E_n}{f_n}}_{\text{signal}} \underbrace{\frac{1}{f_n^2 S_{\rm n}(f_n)}}_{\text{noise}} \dd{f_n}.
% \end{equation}
% It is now useful to inspect the `signal' term in the equation. We can do this specifically by first finding an expression for $\dd{E_n}/\dd{f_n}$ through the chain rule. We can write
% \begin{equation}\label{eq:dedf}
%     \dv{E_n}{f_n} = \dv{E_n}{t} \dv{a}{f_n} \dv{t}{a},
% \end{equation}
% where each term respectively comes from \eqref{eq:edot_peters}, the inverse of \eqref{eq:dfda} and the inverse of \eqref{eq:dadt}.
% We can substitute these into Eq. \ref{eq:dedf} and simplify as follows
% \begin{align}
%     \dv{E_n}{f_n} &= \frac{32}{5} \frac{G^{4}}{c^5} \frac{m_1^2 m_2^2 \qty(m_1 + m_2)}{a^5} g(n, e) \cdot -\frac{4 \pi}{3 n} \frac{a^{5/2}}{(G(m_1 + m_2))^{1/2}} \cdot -\frac{5}{64} \frac{c^5 a^3}{G^3 m_1 m_2 (m_1 + m_2)} \frac{1}{F(e)}, \\
%     &= \frac{2 \pi}{3} \frac{G^{1/2} m_1 m_2}{(m_1 + m_2)^{1/2}} \frac{g(n, e)}{n F(e)} \cdot a^{1/2}, \\
%     &= \frac{2 \pi}{3} \frac{G^{1/2} m_1 m_2}{(m_1 + m_2)^{1/2}} \frac{g(n, e)}{n F(e)} \cdot \qty(\frac{G(m_1 + m_2)}{(2 \pi f_{\rm orb})^2})^{1/6}, \\
%     &= \frac{2^{2/3} \pi^{2/3}}{3} \frac{G^{2/3} m_1 m_2}{(m_1 + m_2)^{1/3}} \frac{g(n, e)}{n F(e)} \cdot f_{\rm orb}^{-1/3}, \\
%     \dv{E_n}{f_n} &= \frac{2^{2/3} \pi^{2/3}}{3} G^{2/3} \mathcal{M}^{5/3} \frac{g(n, e)}{n F(e)} \cdot f_{\rm orb}^{-1/3}.
% \end{align}
% If we further multiply this by the prefactor in \eqref{eq:snr_abs}, we arrive at an expression for the `signal' portion of the equation, which notably is exactly the square of the characteristic strain (see \eqref{eq:char_strain}).
% \begin{equation}
%     \dv{E_n}{f_n} \frac{2 G}{\pi^2 c^3 D_L^2} = \frac{2^{5/3} }{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{n f_{\rm orb}^{1/3}} \frac{g(n, e)}{F(e)} = h_{c,n}^2.
% \end{equation}
% We can therefore write that the sky-averaged signal-to-noise ratio for a Galactic binary is
% \begin{equation}\label{eq:snr_general}
%     \boxed{ \rho^2 = \sum_{n=1}^{\infty}  \int_{f_{n, i}}^{f_{n, f}} \frac{h_{c, n}^2}{f_n^2 S_{\rm n}(f_n)} \dd{f_n}. }
% \end{equation}

% \subsection{Stationary Signal-to-Noise Ratio}
% For our sample, it was extremely useful to note that the vast majority of our binaries were stationary in frequency space on the timescale of a space-based observing mission. In this case, the start and end frequencies are only separated by a very small $\Delta f_n$ and so we can make the approximation that
% \begin{align}
%     \rho_n^2 &= \lim_{\Delta f \to 0} \int_{f_{n}}^{f_{n} + \Delta f_n} \frac{h_{c, n}^2}{f_n^2 S_n(f_n)} \dd{f_n}, \nonumber \\
%     &\approx \frac{\Delta f_n \cdot h_{c, n}^2}{f_n^2 S_n(f_n)}.
% \end{align}
% Moreover, we can immediately write that $\Delta f_n = \dot{f}_n \Delta T$, where we know that $\Delta T = T_{\rm obs}$, such that
% \begin{equation}
%     \rho_n^2 = \left(\frac{\dot{f}_n}{f_n^2} h_{c, n}^2 \right) \frac{T_{\rm obs}}{S_n(f_n)},
% \end{equation}
% where the term in parentheses can be replaced with $2 h_n^2$ using Equation \ref{eq:strain-to-charstrain}. This gives the final expression for the signal-to-noise ratio when the stationary approximation is applied (as shown in Equation \ref{eq:snr_stat})
% \begin{equation}
%     \rho_{\rm stat}^2 = \sum_{n=1}^{\infty} \frac{2 T_{\rm obs} h_n^2}{S_n(f_n)} .
% \end{equation}

@@

\section{Supplementary material}
